---
title: "Interactions by treatment"
author: "Andrew Heiss"
date: "November 16, 2015"
output: 
  html_document: 
    css: fixes.css
    highlight: pygments
    number_sections: yes
    theme: flatly
    toc: yes
    includes:
      in_header: scripts.html
---

```{r setup, include=FALSE}
source("clean_data.R")
knitr::opts_chunk$set(echo = TRUE)
library(broom)
library(ggplot2)
library(scales)
library(stargazer)

# Multiplier for standard error areas
std <- qnorm(0.95 / 2 + 0.5)

report.colors <- c("#E97F01", "#014358")

df.correct <- df.correct %>%
  mutate(in.report = ifelse(tier1 == 0, "Not in report", "In report"),
         in.report = factor(in.report, levels=c("Not in report", "In report"), ordered=TRUE))

df.logit.models <- df.correct %>% 
  filter(lag(adjbicrimlevel) == 0 & year > 2001 & year < 2011)

# Calculate a pseudo R-squared measure using
# 1-\frac{\text{Residual Deviance}}{\text{Null Deviance}}
calc.pseudo.r.squared <- function(x.model) {
  return(round(1 - (x.model$deviance / x.model$null.deviance), 4))
}
```


# Monitoring (presence in the TIP report)

## Democracy × presence in TIP report

### Descriptive

```{r, echo=FALSE, fig.width=8, fig.height=3, warning=FALSE}
prob.crim.democracy.report <- df.correct %>%
  filter(crim1_minus1 == 0, year > 2000) %>%
  # Treatment
  group_by(in.report, fh_cl1) %>%
  summarize(total = n(),
            crim.no = sum(crim1 == 0),
            crim.yes = sum(crim1 == 1),
            prob.yes = crim.yes / total)

ggplot(prob.crim.democracy.report, 
       aes(x=as.factor(fh_cl1), y=prob.yes, fill=in.report)) + 
  geom_bar(stat="identity", position="dodge")
```

```{r, echo=FALSE, fig.width=8, fig.height=3, warning=FALSE}
ggplot(prob.crim.democracy.report, 
       aes(x=fh_cl1, y=prob.yes, colour=in.report)) + 
  geom_line()
```

### Interactions

```{r, results='asis', echo=FALSE}
model.dem.simple <- glm(crim1 ~ fh_cl1 + inreport1 + women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.dem.int <- glm(crim1 ~ fh_cl1 + inreport1 + fh_cl1 * inreport1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("Worse democracy (Freedom House civil liberties)", "In TIP report", 
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "Worse democracy × In TIP report")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.dem.simple, model.dem.int), 
                             calc.pseudo.r.squared)))

stargazer(model.dem.simple, model.dem.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

### Interactions (visualized)

*Note: All covariate values held at their mean or modal values; year held constant at 2005. Rug below indicates actual observed values.*

```{r, echo=FALSE, fig.width=8, fig.height=4, warning=FALSE}
model <- model.dem.int

new.data <- model$model %>%
  select(-fh_cl1) %>%
  group_by(inreport1) %>%
  summarise_each(funs(mean), -(year.factor)) %>%
  mutate(year.factor = factor(2005)) %>%
  right_join(expand.grid(fh_cl1 = seq(1, 7, 0.1), 
                         inreport1 = c(0, 1)), by="inreport1")

plot.predict <- augment(model, newdata=new.data) %>%
  mutate(prob = model$family$linkinv(.fitted),
         prob.lower = model$family$linkinv(.fitted - (std * .se.fit)),
         prob.upper = model$family$linkinv(.fitted + (std * .se.fit)),
         inreport1 = factor(inreport1, labels=c("Not in report", "In report"),
                            ordered=TRUE))

plot.data <- augment(model, type.predict="response") %>%
  rename(prob = .fitted) %>%
  mutate(inreport1 = factor(inreport1, labels=c("Not in report", "In report"),
                            ordered=TRUE))

p.dem.int <- ggplot(plot.predict, aes(x=fh_cl1, y=prob)) +  
  geom_ribbon(aes(ymax=prob.upper, ymin=prob.lower, fill=inreport1), 
              alpha=0.2) + 
  geom_line(aes(colour=inreport1), size=1) +
  geom_rug(data=plot.data, alpha=0.3, size=0.3, sides="b", position="jitter") + 
  labs(x="Worse democracy (Freedom House civil liberties)", 
       y="Predicted probability of criminalization") + 
  scale_y_continuous(labels=percent) + 
  scale_x_continuous(breaks=seq(1, 7, 1)) +
  scale_fill_manual(values=report.colors, name=NULL) + 
  scale_colour_manual(values=report.colors, name=NULL)+
  theme_light()
p.dem.int
```

---

## NGO engagement × presence in TIP report

### Descriptive

```{r, echo=FALSE, fig.width=8, fig.height=3, warning=FALSE}
prob.crim.ngos_ave.report <- df.correct %>%
  filter(crim1_minus1 == 0, year > 2000) %>%
  mutate(ngos_bin = cut(ngos_ave, seq(0, 10, 1))) %>%
  # Treatment
  group_by(in.report, ngos_bin) %>%
  summarize(total = n(),
            crim.no = sum(crim1 == 0),
            crim.yes = sum(crim1 == 1),
            prob.yes = crim.yes / total)

ggplot(prob.crim.ngos_ave.report, 
       aes(x=ngos_bin, y=prob.yes, fill=in.report)) + 
  geom_bar(stat="identity", position="dodge")
```

### Interactions (models)

```{r, results='asis', echo=FALSE}
model.ngo.simple <- glm(crim1 ~ ngos_ave + fh_cl1 + inreport1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.ngo.int <- glm(crim1 ~ ngos_ave + fh_cl1 + inreport1 + 
                         ngos_ave * inreport1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("NGO engagement",
              "Worse democracy (Freedom House civil liberties)", "In TIP report", 
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "NGO engagement × In TIP report")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.ngo.simple, model.ngo.int), 
                             calc.pseudo.r.squared)))

stargazer(model.ngo.simple, model.ngo.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

### Interactions (visualized)

*Note: All covariate values held at their mean or modal values; year held constant at 2005. Rug below indicates actual observed values.*

```{r, echo=FALSE, fig.width=8, fig.height=4, warning=FALSE}
model <- model.ngo.int

new.data <- model$model %>%
  select(-ngos_ave) %>%
  group_by(inreport1) %>%
  summarise_each(funs(mean), -(year.factor)) %>%
  mutate(year.factor = factor(2005)) %>%
  right_join(expand.grid(ngos_ave = seq(0, 10, 0.1), 
                         inreport1 = c(0, 1)), by="inreport1")

plot.predict <- augment(model, newdata=new.data) %>%
  mutate(prob = model$family$linkinv(.fitted),
         prob.lower = model$family$linkinv(.fitted - (std * .se.fit)),
         prob.upper = model$family$linkinv(.fitted + (std * .se.fit)),
         inreport1 = factor(inreport1, labels=c("Not in report", "In report"),
                            ordered=TRUE))

plot.data <- augment(model, type.predict="response") %>%
  rename(prob = .fitted) %>%
  mutate(inreport1 = factor(inreport1, labels=c("Not in report", "In report"),
                            ordered=TRUE))

p.ngo.int <- ggplot(plot.predict, aes(x=ngos_ave, y=prob)) +  
  geom_ribbon(aes(ymax=prob.upper, ymin=prob.lower, fill=inreport1), 
              alpha=0.2) + 
  geom_line(aes(colour=inreport1), size=1) +
  geom_rug(data=plot.data, alpha=0.3, size=0.3, sides="b") + 
  labs(x="NGO engagement", y="Predicted probability of criminalization") + 
  scale_y_continuous(labels=percent) + 
  scale_fill_manual(values=report.colors, name=NULL) + 
  scale_colour_manual(values=report.colors, name=NULL)+
  theme_light()
p.ngo.int
```

---

## Media coverage × presence in TIP report

### Descriptive

### Interactions (models)

```{r, results='asis', echo=FALSE}
model.media.super.basic <- glm(crim1 ~ ht_news_country1 + inreport1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.media.basic <- glm(crim1 ~ ht_news_country1 + inreport1 + 
                          ht_news_country1 * inreport1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.media.simple <- glm(crim1 ~ ht_news_country1 + fh_cl1 + inreport1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.media.int <- glm(crim1 ~ ht_news_country1 + fh_cl1 + inreport1 + 
                         ht_news_country1 * inreport1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))
# bloop <- df.logit.models %>% select(name, year, cowcode, crim1, ht_news_country1, inreport1) %>% mutate(ht_news_country1 * inreport1)
# write_csv(bloop, path="~/Desktop/sample_data.csv", na="")

var.labs <- c("Media coverage",
              "Worse democracy (Freedom House civil liberties)", "In TIP report", 
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "Media coverage × In TIP report")

extra.lines <- list(c("Year fixed effects", c("Yes", "No", "No", "Yes")),
                    c("Pseudo R-squared",
                      sapply(list(model.media.simple, model.media.super.basic,
                                  model.media.basic, model.media.int), 
                             calc.pseudo.r.squared)))

stargazer(model.media.simple, model.media.super.basic, model.media.basic, model.media.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

### Interactions (visualized)

*Note: All covariate values held at their mean or modal values; year held constant at 2005. Rug below indicates actual observed values.*

```{r, echo=FALSE, fig.width=8, fig.height=4, warning=FALSE}
model <- model.media.int

new.data <- model$model %>%
  select(-ht_news_country1) %>%
  group_by(inreport1) %>%
  summarise_each(funs(mean), -(year.factor)) %>%
  mutate(year.factor = factor(2005)) %>%
  right_join(expand.grid(ht_news_country1 = seq(0, 1000, 1), 
                         inreport1 = c(0, 1)), by="inreport1")

plot.predict <- augment(model, newdata=new.data) %>%
  mutate(prob = model$family$linkinv(.fitted),
         prob.lower = model$family$linkinv(.fitted - (std * .se.fit)),
         prob.upper = model$family$linkinv(.fitted + (std * .se.fit)),
         inreport1 = factor(inreport1, labels=c("Not in report", "In report"),
                            ordered=TRUE))

plot.data <- augment(model, type.predict="response") %>%
  rename(prob = .fitted) %>%
  mutate(inreport1 = factor(inreport1, labels=c("Not in report", "In report"),
                            ordered=TRUE))

p.media.int <- ggplot(plot.predict, aes(x=ht_news_country1, y=prob)) +  
  geom_ribbon(aes(ymax=prob.upper, ymin=prob.lower, fill=inreport1), 
              alpha=0.2) + 
  geom_line(aes(colour=inreport1), size=1) +
  geom_rug(data=plot.data, alpha=0.3, size=0.3, sides="b") + 
  labs(x="Media coverage", y="Predicted probability of criminalization") + 
  scale_y_continuous(labels=percent) + 
  scale_fill_manual(values=report.colors, name=NULL) + 
  scale_colour_manual(values=report.colors, name=NULL)+
  theme_light()
p.media.int
```

---

## US foreign aid × presence in TIP report

### Descriptive

### Interactions (models)

```{r, results='asis', echo=FALSE}
model.aid.simple <- glm(crim1 ~ logeconasstP_1 + fh_cl1 + inreport1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.aid.int <- glm(crim1 ~ logeconasstP_1 + fh_cl1 + inreport1 + 
                         logeconasstP_1 * inreport1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("US aid (logged)",
              "Worse democracy (Freedom House civil liberties)", "In TIP report", 
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "US aid × In TIP report")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.aid.simple, model.aid.int), 
                             calc.pseudo.r.squared)))

stargazer(model.aid.simple, model.aid.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

### Interactions (visualized)

*Note: All covariate values held at their mean or modal values; year held constant at 2005. Rug below indicates actual observed values.*

```{r, echo=FALSE, fig.width=8, fig.height=4, warning=FALSE}
model <- model.aid.int

new.data <- model$model %>%
  select(-logeconasstP_1) %>%
  group_by(inreport1) %>%
  summarise_each(funs(mean), -(year.factor)) %>%
  mutate(year.factor = factor(2005)) %>%
  right_join(expand.grid(logeconasstP_1 = seq(0, 23, 0.1), 
                         inreport1 = c(0, 1)), by="inreport1")

plot.predict <- augment(model, newdata=new.data) %>%
  mutate(prob = model$family$linkinv(.fitted),
         prob.lower = model$family$linkinv(.fitted - (std * .se.fit)),
         prob.upper = model$family$linkinv(.fitted + (std * .se.fit)),
         inreport1 = factor(inreport1, labels=c("Not in report", "In report"),
                            ordered=TRUE))

plot.data <- augment(model, type.predict="response") %>%
  rename(prob = .fitted) %>%
  mutate(inreport1 = factor(inreport1, labels=c("Not in report", "In report"),
                            ordered=TRUE))

p.aid.int <- ggplot(plot.predict, aes(x=logeconasstP_1, y=prob)) +  
  geom_ribbon(aes(ymax=prob.upper, ymin=prob.lower, fill=inreport1), 
              alpha=0.2) + 
  geom_line(aes(colour=inreport1), size=1) +
  geom_rug(data=plot.data, alpha=0.3, size=0.3, sides="b") + 
  labs(x="US foreign aid (logged)", y="Predicted probability of criminalization") + 
  scale_y_continuous(labels=percent) + 
  scale_fill_manual(values=report.colors, name=NULL) + 
  scale_colour_manual(values=report.colors, name=NULL)+
  theme_light()
p.aid.int
```

---

## US trade × presence in TIP report

### Descriptive

### Interactions (models)

```{r, results='asis', echo=FALSE}
model.trade.simple <- glm(crim1 ~ newus_tradeshare_gdp + fh_cl1 + inreport1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.trade.int <- glm(crim1 ~ newus_tradeshare_gdp + fh_cl1 + inreport1 + 
                         newus_tradeshare_gdp * inreport1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("Share of US trade (part of GDP)",
              "Worse democracy (Freedom House civil liberties)", "In TIP report", 
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "Trade share × In TIP report")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.trade.simple, model.trade.int), 
                             calc.pseudo.r.squared)))

stargazer(model.trade.simple, model.trade.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

### Interactions (visualized)

*Note: All covariate values held at their mean or modal values; year held constant at 2005. Rug below indicates actual observed values.*

```{r, echo=FALSE, fig.width=8, fig.height=4, warning=FALSE}
model <- model.trade.int

new.data <- model$model %>%
  select(-newus_tradeshare_gdp) %>%
  group_by(inreport1) %>%
  summarise_each(funs(mean), -(year.factor)) %>%
  mutate(year.factor = factor(2005)) %>%
  right_join(expand.grid(newus_tradeshare_gdp = seq(0, 0.6, 0.05), 
                         inreport1 = c(0, 1)), by="inreport1")

plot.predict <- augment(model, newdata=new.data) %>%
  mutate(prob = model$family$linkinv(.fitted),
         prob.lower = model$family$linkinv(.fitted - (std * .se.fit)),
         prob.upper = model$family$linkinv(.fitted + (std * .se.fit)),
         inreport1 = factor(inreport1, labels=c("Not in report", "In report"),
                            ordered=TRUE))

plot.data <- augment(model, type.predict="response") %>%
  rename(prob = .fitted) %>%
  mutate(inreport1 = factor(inreport1, labels=c("Not in report", "In report"),
                            ordered=TRUE))

p.trade.int <- ggplot(plot.predict, aes(x=newus_tradeshare_gdp, y=prob)) +  
  geom_ribbon(aes(ymax=prob.upper, ymin=prob.lower, fill=inreport1), 
              alpha=0.2) + 
  geom_line(aes(colour=inreport1), size=1) +
  geom_rug(data=plot.data, alpha=0.3, size=0.3, sides="b") + 
  labs(x="Trade with US (percent of GDP)", 
       y="Predicted probability of criminalization") + 
  scale_y_continuous(labels=percent) + 
  scale_fill_manual(values=report.colors, name=NULL) + 
  scale_colour_manual(values=report.colors, name=NULL)+
  theme_light()
p.trade.int
```

---

## Protocol ratified × presence in TIP report

### Descriptive

### Interactions (models)

```{r, results='asis', echo=FALSE}
model.rat.simple <- glm(crim1 ~ fh_cl1 + inreport1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.rat.int <- glm(crim1 ~ fh_cl1 + inreport1 + 
                         ratproto2000_1 * inreport1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("Worse democracy (Freedom House civil liberties)", "In TIP report", 
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "Protocol ratification × In TIP report")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.rat.simple, model.rat.int), 
                             calc.pseudo.r.squared)))

stargazer(model.rat.simple, model.rat.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

### Interactions (visualized)

*Note: All covariate values held at their mean or modal values; year held constant at 2005.*

```{r, echo=FALSE, fig.width=8, fig.height=4, warning=FALSE}
model <- model.rat.int

new.data <- model$model %>%
  select(-ratproto2000_1) %>%
  group_by(inreport1) %>%
  summarise_each(funs(mean), -(year.factor)) %>%
  mutate(year.factor = factor(2005)) %>%
  right_join(expand.grid(ratproto2000_1 = c(0, 1), 
                         inreport1 = c(0, 1)), by="inreport1")

plot.predict <- augment(model, newdata=new.data) %>%
  mutate(prob = model$family$linkinv(.fitted),
         prob.lower = model$family$linkinv(.fitted - (std * .se.fit)),
         prob.upper = model$family$linkinv(.fitted + (std * .se.fit)),
         inreport1 = factor(inreport1, labels=c("Not in report", "In report"),
                            ordered=TRUE),
         ratproto2000_1 = factor(ratproto2000_1, 
                                 labels=c("Not ratified", "Ratified"), 
                                 ordered=TRUE))

plot.data <- augment(model, type.predict="response") %>%
  rename(prob = .fitted) %>%
  mutate(inreport1 = factor(inreport1, labels=c("Not in report", "In report"),
                            ordered=TRUE))

p.rat.int <- ggplot(plot.predict, aes(x=ratproto2000_1, y=prob, colour=inreport1)) + 
  geom_pointrange(aes(ymax=prob.upper, ymin=prob.lower), size=.75,
                  position=position_dodge(width=0.25)) + 
  labs(x="2000 TIP protocol ratification", 
       y="Predicted probability of criminalization") + 
  scale_y_continuous(labels=percent) + 
  scale_colour_manual(values=report.colors, name=NULL)+
  theme_light()
p.rat.int
```

---

## Wikileaks engagement/intensity × presence in TIP report

### Descriptive

### Interactions (models)

```{r, results='asis', echo=FALSE}
model.wl.simple <- glm(crim1 ~ prop_tip_wl1 + fh_cl1 + inreport1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.wl.int <- glm(crim1 ~ prop_tip_wl1 + fh_cl1 + inreport1 + 
                         prop_tip_wl1 * inreport1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("Proportion of TIP-related cables (observed in Wikileaks)",
              "Worse democracy (Freedom House civil liberties)", "In TIP report", 
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "TIP cables × In TIP report")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.wl.simple, model.wl.int), 
                             calc.pseudo.r.squared)))

stargazer(model.wl.simple, model.wl.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

### Interactions (visualized)

*Note: All covariate values held at their mean or modal values; year held constant at 2005. Rug below indicates actual observed values.*

```{r, echo=FALSE, fig.width=8, fig.height=4, warning=FALSE}
model <- model.wl.int

new.data <- model$model %>%
  select(-prop_tip_wl1) %>%
  group_by(inreport1) %>%
  summarise_each(funs(mean), -(year.factor)) %>%
  mutate(year.factor = factor(2005)) %>%
  right_join(expand.grid(prop_tip_wl1 = seq(0, 1, 0.05), 
                         inreport1 = c(0, 1)), by="inreport1")

plot.predict <- augment(model, newdata=new.data) %>%
  mutate(prob = model$family$linkinv(.fitted),
         prob.lower = model$family$linkinv(.fitted - (std * .se.fit)),
         prob.upper = model$family$linkinv(.fitted + (std * .se.fit)),
         inreport1 = factor(inreport1, labels=c("Not in report", "In report"),
                            ordered=TRUE))

plot.data <- augment(model, type.predict="response") %>%
  rename(prob = .fitted) %>%
  mutate(inreport1 = factor(inreport1, labels=c("Not in report", "In report"),
                            ordered=TRUE))

p.wl.int <- ggplot(plot.predict, aes(x=prop_tip_wl1, y=prob)) +  
  geom_ribbon(aes(ymax=prob.upper, ymin=prob.lower, fill=inreport1), 
              alpha=0.2) + 
  geom_line(aes(colour=inreport1), size=1) +
  geom_rug(data=plot.data, alpha=0.3, size=0.3, sides="b") + 
  labs(x="Proportion of TIP-related cables (observed in Wikileaks)", 
       y="Predicted probability of criminalization") + 
  scale_y_continuous(labels=percent) + 
  scale_fill_manual(values=report.colors, name=NULL) + 
  scale_colour_manual(values=report.colors, name=NULL)+
  theme_light()
p.wl.int
```

---

## TIP NGO count × presence in TIP report

### Descriptive

### Interactions (models)

```{r, results='asis', echo=FALSE}
model.ngo.new.simple <- glm(crim1 ~ ht_ngos + fh_cl1 + inreport1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.ngo.new.int <- glm(crim1 ~ ht_ngos + fh_cl1 + inreport1 + 
                         ht_ngos * inreport1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("Number of anti-TIP NGOs",
              "Worse democracy (Freedom House civil liberties)", "In TIP report", 
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "TIP cables × In TIP report")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.ngo.new.simple, model.ngo.new.int), 
                             calc.pseudo.r.squared)))

stargazer(model.ngo.new.simple, model.ngo.new.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

### Interactions (visualized)

*Note: All covariate values held at their mean or modal values; year held constant at 2005. Rug below indicates actual observed values.*

```{r, echo=FALSE, fig.width=8, fig.height=4, warning=FALSE}
model <- model.ngo.new.int

new.data <- model$model %>%
  select(-ht_ngos) %>%
  group_by(inreport1) %>%
  summarise_each(funs(mean), -(year.factor)) %>%
  mutate(year.factor = factor(2005)) %>%
  right_join(expand.grid(ht_ngos = seq(0, 100, 0.5), 
                         inreport1 = c(0, 1)), by="inreport1")

plot.predict <- augment(model, newdata=new.data) %>%
  mutate(prob = model$family$linkinv(.fitted),
         prob.lower = model$family$linkinv(.fitted - (std * .se.fit)),
         prob.upper = model$family$linkinv(.fitted + (std * .se.fit)),
         inreport1 = factor(inreport1, labels=c("Not in report", "In report"),
                            ordered=TRUE))

plot.data <- augment(model, type.predict="response") %>%
  rename(prob = .fitted) %>%
  mutate(inreport1 = factor(inreport1, labels=c("Not in report", "In report"),
                            ordered=TRUE))

p.ngo.new.int <- ggplot(plot.predict, aes(x=ht_ngos, y=prob)) +  
  geom_ribbon(aes(ymax=prob.upper, ymin=prob.lower, fill=inreport1), 
              alpha=0.2) + 
  geom_line(aes(colour=inreport1), size=1) +
  geom_rug(data=plot.data, alpha=0.3, size=0.3, sides="b") + 
  labs(x="Number of anti-TIP NGOs", 
       y="Predicted probability of criminalization") + 
  scale_y_continuous(labels=percent) + 
  scale_fill_manual(values=report.colors, name=NULL) + 
  scale_colour_manual(values=report.colors, name=NULL)+
  theme_light()
p.ngo.new.int
```

---

## TIP funding from US × presence in TIP report

### Descriptive

### Interactions (models)

```{r, results='asis', echo=FALSE}
model.funding.simple <- glm(crim1 ~ log.total.funding1 + fh_cl1 + inreport1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.funding.int <- glm(crim1 ~ log.total.funding1 + fh_cl1 + inreport1 + 
                         log.total.funding1 * inreport1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("Total anti-TIP funding from US (log)",
              "Worse democracy (Freedom House civil liberties)", "In TIP report", 
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "TIP cables × In TIP report")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.funding.simple, model.funding.int), 
                             calc.pseudo.r.squared)))

stargazer(model.funding.simple, model.funding.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

### Interactions (visualized)

*Note: All covariate values held at their mean or modal values; year held constant at 2005. Rug below indicates actual observed values.*

```{r, echo=FALSE, fig.width=8, fig.height=4, warning=FALSE}
model <- model.funding.int

new.data <- model$model %>%
  select(-log.total.funding1) %>%
  group_by(inreport1) %>%
  summarise_each(funs(mean), -(year.factor)) %>%
  mutate(year.factor = factor(2005)) %>%
  right_join(expand.grid(log.total.funding1 = seq(0, 16, 0.5), 
                         inreport1 = c(0, 1)), by="inreport1")

plot.predict <- augment(model, newdata=new.data) %>%
  mutate(prob = model$family$linkinv(.fitted),
         prob.lower = model$family$linkinv(.fitted - (std * .se.fit)),
         prob.upper = model$family$linkinv(.fitted + (std * .se.fit)),
         inreport1 = factor(inreport1, labels=c("Not in report", "In report"),
                            ordered=TRUE))

plot.data <- augment(model, type.predict="response") %>%
  rename(prob = .fitted) %>%
  mutate(inreport1 = factor(inreport1, labels=c("Not in report", "In report"),
                            ordered=TRUE))

p.funding.int <- ggplot(plot.predict, aes(x=log.total.funding1, y=prob)) +  
  geom_ribbon(aes(ymax=prob.upper, ymin=prob.lower, fill=inreport1), 
              alpha=0.2) + 
  geom_line(aes(colour=inreport1), size=1) +
  geom_rug(data=plot.data, alpha=0.3, size=0.3, sides="b") + 
  labs(x="Total anti-TIP funding from US (log)", 
       y="Predicted probability of criminalization") + 
  scale_y_continuous(labels=percent) + 
  scale_fill_manual(values=report.colors, name=NULL) + 
  scale_colour_manual(values=report.colors, name=NULL)+
  theme_light()
p.funding.int
```

---

# Lower tier ratings

## Democracy × lower tier ratings

```{r, echo=FALSE, fig.width=8, fig.height=3, warning=FALSE}
prob.crim.democracy.rating <- df.correct %>%
  filter(crim1_minus1 == 0, year > 2000) %>%
  # Treatment
  mutate(lower.rating = ifelse(tier1 %in% c(1, 2, 2.5), "1, 2, or 2.5", "3")) %>%
  group_by(lower.rating, fh_cl1) %>%
  summarize(total = n(),
            crim.no = sum(crim1 == 0),
            crim.yes = sum(crim1 == 1),
            prob.yes = crim.yes / total)

ggplot(prob.crim.democracy.rating, 
       aes(x=as.factor(fh_cl1), y=prob.yes, fill=lower.rating)) + 
  geom_bar(stat="identity", position="dodge")
```

### Descriptive

### Split sample

### Interactions

```{r, results='asis', echo=FALSE}
model.dem.simple <- glm(crim1 ~ fh_cl1 + low_tier1 + women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.dem.int <- glm(crim1 ~ fh_cl1 + low_tier1 + fh_cl1 * low_tier1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("Worse democracy (Freedom House civil liberties)", "Lowest tier", 
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "Worse democracy × Lowest tier")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.dem.simple, model.dem.int), 
                             calc.pseudo.r.squared)))

stargazer(model.dem.simple, model.dem.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

---

## NGO engagement × lower tier ratings

### Descriptive

### Split sample

### Interactions

```{r, results='asis', echo=FALSE}
model.ngo.simple <- glm(crim1 ~ ngos_ave + fh_cl1 + low_tier1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.ngo.int <- glm(crim1 ~ ngos_ave + fh_cl1 + low_tier1 + 
                         ngos_ave * low_tier1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("NGO engagement",
              "Worse democracy (Freedom House civil liberties)", "Lowest tier", 
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "NGO engagement × Lowest tier")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.ngo.simple, model.ngo.int), 
                             calc.pseudo.r.squared)))

stargazer(model.ngo.simple, model.ngo.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

---

## Media coverage × lower tier ratings

### Descriptive

### Split sample

### Interactions

```{r, results='asis', echo=FALSE}
model.media.simple <- glm(crim1 ~ ht_news_country1 + fh_cl1 + low_tier1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.media.int <- glm(crim1 ~ ht_news_country1 + fh_cl1 + low_tier1 + 
                         ht_news_country1 * low_tier1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("Media coverage",
              "Worse democracy (Freedom House civil liberties)", "Lowest tier", 
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "Media coverage × Lowest tier")

extra.lines <- list(c("Year fixed effects", c("Yes", "Yes")),
                    c("Pseudo R-squared",
                      sapply(list(model.media.simple, model.media.int), 
                             calc.pseudo.r.squared)))

stargazer(model.media.simple,  model.media.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

---

## US foreign aid × lower tier ratings

### Descriptive

### Split sample

### Interactions

```{r, results='asis', echo=FALSE}
model.aid.simple <- glm(crim1 ~ logeconasstP_1 + fh_cl1 + low_tier1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.aid.int <- glm(crim1 ~ logeconasstP_1 + fh_cl1 + low_tier1 + 
                         logeconasstP_1 * low_tier1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("US aid (logged)",
              "Worse democracy (Freedom House civil liberties)", "Lowest tier", 
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "US aid × Lowest tier")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.aid.simple, model.aid.int), 
                             calc.pseudo.r.squared)))

stargazer(model.aid.simple, model.aid.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

---

## US trade × lower tier ratings

### Descriptive

### Split sample

### Interactions

```{r, results='asis', echo=FALSE}
model.trade.simple <- glm(crim1 ~ newus_tradeshare_gdp + fh_cl1 + low_tier1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.trade.int <- glm(crim1 ~ newus_tradeshare_gdp + fh_cl1 + low_tier1 + 
                         newus_tradeshare_gdp * low_tier1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("Share of US trade (part of GDP)",
              "Worse democracy (Freedom House civil liberties)", "Lowest tier", 
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "Trade share × Lowest tier")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.trade.simple, model.trade.int), 
                             calc.pseudo.r.squared)))

stargazer(model.trade.simple, model.trade.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

---

## Protocol ratified × lower tier ratings

### Descriptive

### Split sample

### Interactions

```{r, results='asis', echo=FALSE}
model.rat.simple <- glm(crim1 ~ fh_cl1 + low_tier1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.rat.int <- glm(crim1 ~ fh_cl1 + low_tier1 + 
                         ratproto2000_1 * low_tier1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("Worse democracy (Freedom House civil liberties)", "Lowest tier", 
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "Protocol ratification × Lowest tier")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.rat.simple, model.rat.int), 
                             calc.pseudo.r.squared)))

stargazer(model.rat.simple, model.rat.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

---

## Wikileaks engagement/intensity × lower tier ratings

### Descriptive

### Split sample

### Interactions

```{r, results='asis', echo=FALSE}
model.wl.simple <- glm(crim1 ~ prop_tip_wl1 + fh_cl1 + low_tier1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.wl.int <- glm(crim1 ~ prop_tip_wl1 + fh_cl1 + low_tier1 + 
                         prop_tip_wl1 * low_tier1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("Proportion of TIP-related cables (observed in Wikileaks)",
              "Worse democracy (Freedom House civil liberties)", "Lowest tier", 
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "TIP cables × Lowest tier")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.wl.simple, model.wl.int), 
                             calc.pseudo.r.squared)))

stargazer(model.wl.simple, model.wl.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

---

## TIP NGO count × lower tier ratings

### Descriptive

### Split sample

### Interactions

```{r, results='asis', echo=FALSE}
model.ngo.new.simple <- glm(crim1 ~ ht_ngos + fh_cl1 + low_tier1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.ngo.new.int <- glm(crim1 ~ ht_ngos + fh_cl1 + low_tier1 + 
                         ht_ngos * low_tier1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("Number of anti-TIP NGOs",
              "Worse democracy (Freedom House civil liberties)", "Lowest tier", 
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "TIP cables × Lowest tier")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.ngo.new.simple, model.ngo.new.int), 
                             calc.pseudo.r.squared)))

stargazer(model.ngo.new.simple, model.ngo.new.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

---

## TIP funding from US × lower tier ratings

### Descriptive

### Split sample

### Interactions

```{r, results='asis', echo=FALSE}
model.funding.simple <- glm(crim1 ~ total.funding1 + fh_cl1 + low_tier1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.funding.int <- glm(crim1 ~ total.funding1 + fh_cl1 + low_tier1 + 
                         total.funding1 * low_tier1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("Total anti-TIP funding from US",
              "Worse democracy (Freedom House civil liberties)", "Lowest tier", 
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "TIP cables × Lowest tier")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.funding.simple, model.funding.int), 
                             calc.pseudo.r.squared)))

stargazer(model.funding.simple, model.funding.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

---

# Downgrading

## Democracy × downgrading

```{r, echo=FALSE, fig.width=8, fig.height=3, warning=FALSE}
prob.crim.democracy.down <- df.correct %>%
  filter(crim1_minus1 == 0, year > 2000) %>%
  # Treatment
  mutate(downgrade = factor(worsen_tier1)) %>%
  group_by(downgrade, fh_cl1) %>%
  summarize(total = n(),
            crim.no = sum(crim1 == 0),
            crim.yes = sum(crim1 == 1),
            prob.yes = crim.yes / total)

ggplot(prob.crim.democracy.down, 
       aes(x=as.factor(fh_cl1), y=prob.yes, fill=downgrade)) + 
  geom_bar(stat="identity", position="dodge")
```

### Descriptive

### Split sample

### Interactions

```{r, results='asis', echo=FALSE}
model.dem.simple <- glm(crim1 ~ fh_cl1 + 
                        new_watch3 + new_watch2 + new_watch1 + 
                        women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.dem.int <- glm(crim1 ~ fh_cl1 + 
                     new_watch3 + new_watch2 + new_watch1 + 
                     fh_cl1 * new_watch3 + 
                     fh_cl1 * new_watch2 + 
                     fh_cl1 * new_watch1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("Worse democracy (Freedom House civil liberties)", 
              "First demotion (t−3)", "First demotion (t−2)", 
              "First demotion (t−1)",
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "Worse democracy × First demotion (t−3)", 
              "Worse democracy × First demotion (t−2)", 
              "Worse democracy × First demotion (t−1)")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.dem.simple, model.dem.int), 
                             calc.pseudo.r.squared)))

stargazer(model.dem.simple, model.dem.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

---

## NGO engagement × downgrading

### Descriptive

### Split sample

### Interactions

```{r, results='asis', echo=FALSE}
model.ngo.simple <- glm(crim1 ~ ngos_ave + fh_cl1 + 
                        new_watch3 + new_watch2 + new_watch1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.ngo.int <- glm(crim1 ~ ngos_ave + fh_cl1 + 
                     new_watch3 + new_watch2 + new_watch1 + 
                     ngos_ave * new_watch3 + 
                     ngos_ave * new_watch2 + 
                     ngos_ave * new_watch1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("NGO engagement",
              "Worse democracy (Freedom House civil liberties)", 
              "First demotion (t−3)", "First demotion (t−2)", 
              "First demotion (t−1)",
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "Worse democracy × First demotion (t−3)", 
              "Worse democracy × First demotion (t−2)", 
              "Worse democracy × First demotion (t−1)")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.ngo.simple, model.ngo.int), 
                             calc.pseudo.r.squared)))

stargazer(model.ngo.simple, model.ngo.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

---

## Media coverage × downgrading

### Descriptive

### Split sample

### Interactions

```{r, results='asis', echo=FALSE}
model.media.simple <- glm(crim1 ~ ht_news_country1 + fh_cl1 + 
                          new_watch3 + new_watch2 + new_watch1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.media.int <- glm(crim1 ~ ht_news_country1 + fh_cl1 + 
                       new_watch3 + new_watch2 + new_watch1 + 
                     ht_news_country1 * new_watch3 + 
                     ht_news_country1 * new_watch2 + 
                     ht_news_country1 * new_watch1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("Media coverage",
              "Worse democracy (Freedom House civil liberties)", 
              "First demotion (t−3)", "First demotion (t−2)", 
              "First demotion (t−1)",
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "Worse democracy × First demotion (t−3)", 
              "Worse democracy × First demotion (t−2)", 
              "Worse democracy × First demotion (t−1)")

extra.lines <- list(c("Year fixed effects", c("Yes", "Yes")),
                    c("Pseudo R-squared",
                      sapply(list(model.media.simple, model.media.int), 
                             calc.pseudo.r.squared)))

stargazer(model.media.simple,  model.media.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

---

## US foreign aid × downgrading

### Descriptive

### Split sample

### Interactions

```{r, results='asis', echo=FALSE}
model.aid.simple <- glm(crim1 ~ logeconasstP_1 + fh_cl1 + 
                        new_watch3 + new_watch2 + new_watch1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.aid.int <- glm(crim1 ~ logeconasstP_1 + fh_cl1 + 
                     new_watch3 + new_watch2 + new_watch1 + 
                     logeconasstP_1 * new_watch3 + 
                     logeconasstP_1 * new_watch2 + 
                     logeconasstP_1 * new_watch1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("US aid (logged)",
              "Worse democracy (Freedom House civil liberties)", 
              "First demotion (t−3)", "First demotion (t−2)", 
              "First demotion (t−1)",
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "Worse democracy × First demotion (t−3)", 
              "Worse democracy × First demotion (t−2)", 
              "Worse democracy × First demotion (t−1)")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.aid.simple, model.aid.int), 
                             calc.pseudo.r.squared)))

stargazer(model.aid.simple, model.aid.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

---

## US trade × downgrading

### Descriptive

### Split sample

### Interactions

```{r, results='asis', echo=FALSE}
model.trade.simple <- glm(crim1 ~ newus_tradeshare_gdp + fh_cl1 +
                          new_watch3 + new_watch2 + new_watch1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.trade.int <- glm(crim1 ~ newus_tradeshare_gdp + fh_cl1 +
                       new_watch3 + new_watch2 + new_watch1 + 
                     newus_tradeshare_gdp * new_watch3 + 
                     newus_tradeshare_gdp * new_watch2 + 
                     newus_tradeshare_gdp * new_watch1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("Share of US trade (part of GDP)",
              "Worse democracy (Freedom House civil liberties)", 
              "First demotion (t−3)", "First demotion (t−2)", 
              "First demotion (t−1)",
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "Worse democracy × First demotion (t−3)", 
              "Worse democracy × First demotion (t−2)", 
              "Worse democracy × First demotion (t−1)")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.trade.simple, model.trade.int), 
                             calc.pseudo.r.squared)))

stargazer(model.trade.simple, model.trade.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

---

## Protocol ratified × downgrading

### Descriptive

### Split sample

### Interactions

```{r, results='asis', echo=FALSE}
model.rat.simple <- glm(crim1 ~ fh_cl1 + 
                        new_watch3 + new_watch2 + new_watch1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.rat.int <- glm(crim1 ~ fh_cl1 + 
                     new_watch3 + new_watch2 + new_watch1 + 
                     ratproto2000_1 * new_watch3 + 
                     ratproto2000_1 * new_watch2 + 
                     ratproto2000_1 * new_watch1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("Worse democracy (Freedom House civil liberties)", 
              "First demotion (t−3)", "First demotion (t−2)", 
              "First demotion (t−1)",
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "Worse democracy × First demotion (t−3)", 
              "Worse democracy × First demotion (t−2)", 
              "Worse democracy × First demotion (t−1)")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.rat.simple, model.rat.int), 
                             calc.pseudo.r.squared)))

stargazer(model.rat.simple, model.rat.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

---

## Wikileaks engagement/intensity × downgrading

### Descriptive

### Split sample

### Interactions

```{r, results='asis', echo=FALSE}
model.wl.simple <- glm(crim1 ~ prop_tip_wl1 + fh_cl1 + 
                       new_watch3 + new_watch2 + new_watch1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.wl.int <- glm(crim1 ~ prop_tip_wl1 + fh_cl1 + 
                    new_watch3 + new_watch2 + new_watch1 + 
                     prop_tip_wl1 * new_watch3 + 
                     prop_tip_wl1 * new_watch2 + 
                     prop_tip_wl1 * new_watch1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("Proportion of TIP-related cables (observed in Wikileaks)",
              "Worse democracy (Freedom House civil liberties)", 
              "First demotion (t−3)", "First demotion (t−2)", 
              "First demotion (t−1)",
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "Worse democracy × First demotion (t−3)", 
              "Worse democracy × First demotion (t−2)", 
              "Worse democracy × First demotion (t−1)")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.wl.simple, model.wl.int), 
                             calc.pseudo.r.squared)))

stargazer(model.wl.simple, model.wl.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

---

## TIP NGO count × downgrading

### Descriptive

### Split sample

### Interactions

```{r, results='asis', echo=FALSE}
model.ngo.new.simple <- glm(crim1 ~ ht_ngos + fh_cl1 + 
                            new_watch3 + new_watch2 + new_watch1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.ngo.new.int <- glm(crim1 ~ ht_ngos + fh_cl1 + 
                         new_watch3 + new_watch2 + new_watch1 + 
                     ht_ngos * new_watch3 + 
                     ht_ngos * new_watch2 + 
                     ht_ngos * new_watch1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("Number of anti-TIP NGOs",
              "Worse democracy (Freedom House civil liberties)", 
              "First demotion (t−3)", "First demotion (t−2)", 
              "First demotion (t−1)",
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "Worse democracy × First demotion (t−3)", 
              "Worse democracy × First demotion (t−2)", 
              "Worse democracy × First demotion (t−1)")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.ngo.new.simple, model.ngo.new.int), 
                             calc.pseudo.r.squared)))

stargazer(model.ngo.new.simple, model.ngo.new.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```

---

## TIP funding from US × downgrading

### Descriptive

### Split sample

### Interactions

```{r, results='asis', echo=FALSE}
model.funding.simple <- glm(crim1 ~ total.funding1 + fh_cl1 + 
                            new_watch3 + new_watch2 + new_watch1 + 
                          women1 + ratproto2000_1 + 
                    corrected_regcrim1_1 + missinfo8_2 + year.factor,# + 
                    # bigaid1 + logpop_1 + loggdppercap_1 + corruption_1,
                  data=df.logit.models,
                  family=binomial(link="logit"))
model.funding.int <- glm(crim1 ~ total.funding1 + fh_cl1 + 
                         new_watch3 + new_watch2 + new_watch1 + 
                     total.funding1 * new_watch3 + 
                     total.funding1 * new_watch2 + 
                     total.funding1 * new_watch1 + 
                           women1 + ratproto2000_1 + 
                           corrected_regcrim1_1 + missinfo8_2 + year.factor,
                         data=df.logit.models,
                         family=binomial(link="logit"))

var.labs <- c("Total anti-TIP funding from US",
              "Worse democracy (Freedom House civil liberties)", 
              "First demotion (t−3)", "First demotion (t−2)", 
              "First demotion (t−1)",
              "Share of women in parliament", 
              "2000 TIP protocol ratification", 
              "Regional density of criminalization",
              "Missing info",
              "Worse democracy × First demotion (t−3)", 
              "Worse democracy × First demotion (t−2)", 
              "Worse democracy × First demotion (t−1)")

extra.lines <- list(c("Year fixed effects", rep("Yes", 2)),
                    c("Pseudo R-squared",
                      sapply(list(model.funding.simple, model.funding.int), 
                             calc.pseudo.r.squared)))

stargazer(model.funding.simple, model.funding.int,
          covariate.labels=var.labs, 
          dep.var.labels.include=FALSE,
          dep.var.caption="Criminalization",
          apply.coef=exp, type="html", p.auto=FALSE, omit="year\\.factor",
          keep.stat=c("n", "ll"), 
          notes.align="l", add.lines=extra.lines,
          notes=c("Log odds reported; standard errors in parentheses. All explanatory variables are lagged one period unless otherwise noted."))
```
